---
title: "0220_meeting"
author: "Xinyao Wu"
date: "2/20/2020"
output: 
  html_document:
    number_sections: false
    code_folding: hide
    toc: True
    toc_float: True
---
```{r include=FALSE}
library(tidyverse)
library(MASS)
set.seed(1234)
```


#Tasks

##1. Multi-variable propensity score paper

[A Tutorial on Propensity Score Estimation for Multiple Treatments Using Generalized Boosted Models](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3710547/)

[propensity score review, mentioned multi-exposure](http://citeseerx.ist.psu.edu/viewdoc/download;jsessionid=F25259B79B97955D0C16BD7529683CCE?doi=10.1.1.128.8840&rep=rep1&type=pdf)

[Adaptive contrast weighted learning for multi‐stage multi‐treatment decision‐making](https://onlinelibrary.wiley.com/doi/epdf/10.1111/biom.12539)

##2. Fill in the blank of last meeting codes\

##3. Sim = 10, plot the bias\


##4. Think carefully the difference of simulation and bootstrap

#Instructions

1. population = 10,000,000, sample(n=825) from pop.\


2. Use population to measure true ATE


3. RE-calculate the ATE.(Formula is wrong last week). Use 75th and 25th percentile for each mental.

4. To calculate the estimated ATE in each simulation:\
   *(1) generate data*
   
```{r}
#confoundings
age = rnorm(825,22.9,4.2)
iq = rnorm(825,26,5)
edu = rbinom(825,1,0.24)
smoke = rbinom(825,1,0.24)

#exposure

as = age^(1/2)+age*iq+edu+smoke^2+rnorm(825,0,5)
mn = age*2+edu^2+iq+smoke^3+rnorm(825,0,5)
pb = age+iq*edu+iq*smoke+smoke^2+rnorm(825,0,5)

##quantile

quantile(as,probs = c(0.25,0.75))
quantile(mn,probs = c(0.25,0.75))
quantile(pb,probs = c(0.25,0.75))

##assume coef
par(mfrow=c(2,2))
cs = 5*as+7*mn-3*pb+age*iq+edu*iq+smoke^2 +rnorm(825,sd = 35)

hist(cs)
hist(pb)
hist(mn)
hist(as)
```
 *(1)-2 calculate ATE*
 

E[Y|As= 75th percentile of As distribution, Mn= 75th percentile of Mn distribution, Ps= 75th percentile of Ps distribution]-E[Y|As= 75th percentile of As distribution, Mn= 75th percentile of Mn distribution, Ps= 75th percentile of Ps distribution]


   *(2) linear regression*
```{r}
#propensity score
fit.as = lm(as~age+iq+as.factor(edu)+as.factor(smoke))
fit.mn = lm(mn~age+iq+as.factor(edu)+as.factor(smoke))
fit.pb = lm(pb~age+iq+as.factor(edu)+as.factor(smoke))
summary(fit.as)
summary(fit.mn)
summary(fit.pb)
#Y~AX+C
df = data.frame(cs,as,mn,pb,age,iq,edu,smoke)
fit = lm(cs~as+mn+pb+age+iq+as.factor(edu)+as.factor(smoke),data = df)
summary(fit)
```

*(3) apply coef to generated obs, then calculate the 75th and 25th for each point*\
   
```{r}
#predict exposures
as.hat = predict(fit.as)
mn.hat = predict(fit.mn)
pb.hat = predict(fit.pb)

quantile(as.hat,c(0.25,0.75))
quantile(mn.hat,c(0.25,0.75))
quantile(pb.hat,c(0.25,0.75))
```
   
   *(4) estimate Y*
```{r}
# Y|75% exposure
as = rep(689,825)
mn = rep(78.94541 ,825)
pb = rep(48.83487,825)
new75 = data.frame(as,mn,pb,age,iq,edu,smoke)
y75.hat = predict(fit,new75,type = 'response')

# Y|75% exposure
as = rep(496.6899,825)
mn = rep(65.43030,825)
pb = rep(21.62003,825)
new25 = data.frame(as,mn,pb,age,iq,edu,smoke)
y25.hat = predict.lm(fit,newdata = new25,type = 'response')

par(mfrow = c(1,2))
hist(y75.hat)
hist(y25.hat)
```
   
   
   *(5) take average*\
   
```{r}
ATE  = mean(y75.hat)-mean(y25.hat)
print(ATE)
```
   



#review

1. What is the difference of the use of simulation and bootstrap? \
simulation--point esitimate\
bootstrap-- sd 

2.What is the difference of correlated and interacted? \

Y = A+B+B*C \
A = 3B+2 \

A and B are correlated. B and C are interacted.









