---
title: "coding0304"
author: "Xinyao Wu"
date: "3/4/2020"
output: 
  html_document:
    number_sections: false
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(MASS)
library(twang)
library(CBPS)
```

##Data generation

```{r}
data_generation = function(){
#confoundings
age = rnorm(825,22.9,4.2)
iq = rnorm(825,26,5)
edu = rbinom(825,1,0.24)
smoke = rbinom(825,1,0.8)
obs = data.frame(age,iq,edu,smoke)
#a
as = age*0.002+iq*0.02+edu*0.02+smoke*0.1+rnorm(825,0,0.05)
mn = 0.043*as+age*0.02+edu*0.02+iq*0.02+smoke*0.02+rnorm(825,0,0.05)
pb = 0.04*mn+age*0.02+edu*0.02+iq*0.02+smoke*0.02+rnorm(825,0,0.02)
#y
cs = -0.05*as-0.7*mn-0.023*pb+iq+age+edu+0.01*age*iq+0.01*edu*iq-smoke +rnorm(825,0,sd = 0.03)
df = data.frame(as,mn,pb,obs,cs)
return(df)
}
###test = data_generation()

```

## ACE calculation function(regression)
```{r regression}
re.est = function(df,n){
### Method1. Regression 
  
fit = lm(cs~as+mn+pb+age*iq+as.factor(edu)*iq+as.factor(smoke)^2,data = df)

obs = df[4:7]
as = pull(df,as)
mn = pull(df,mn)
pb = pull(df,pb)

as.q = quantile(as,c(0.25,0.75))
mn.q = quantile(mn,c(0.25,0.75))
pb.q = quantile(pb,c(0.25,0.75))

as = rep(as.q[1],n)
mn = rep(mn.q[1],n)
pb = rep(pb.q[1],n)
new1 = data.frame(as,mn,pb,obs)
yhat_25 = predict(fit,new1,type = 'response')

as = rep(as.q[2],n)
mn = rep(mn.q[2],n)
pb = rep(pb.q[2],n)
new2 = data.frame(as,mn,pb,obs)
yhat_75 = predict(fit,new2,type = 'response')

ace = mean(yhat_75)-mean(yhat_25)
return(ace)

}
```

###Method2. MSM(function)

[IPW reference](https://meghapsimatrix.com/post/continuous-r-rmarkdown/)

```{r}

ipw = function(x,df,form){
# the numerator
mod_num <- lm(x ~ 1, data = df)

num <- dnorm(x = x, # treatment 
             mean = fitted.values(mod_num), # fitted values
             sd = summary(mod_num)$sigma) # model sigma
# the demonimator
mod_den <- lm(formula = form, data = df)

den <- dnorm(x = x, # treatment variable
             mean = fitted.values(mod_den), # fitted values
             sd = summary(mod_den)$sigma)
ipw_s = num/den
return(ipw_s)
}

```

### Marginal Structure Model

```{r}
msm.mann = function(data = df){
#test
form1 = 'as~age+iq+as.factor(edu)+as.factor(smoke)'
form2 = 'mn~as+age+iq+as.factor(edu)+as.factor(smoke)'
form3 = 'pb~as+age+iq+as.factor(edu)+as.factor(smoke)'
asw = ipw(df$as,df,form1)
mnw = ipw(df$mn,df,form2)
pbw = ipw(df$pb,df,form3)

#weight matrix
weight.matrix = asw*mnw*pbw

msm <-svyglm(cs~as+mn+pb,design = svydesign(~ 1, weights = ~ weight.matrix,data=df))
co = coef(msm)


#predict

est2 = co['as']*(quantile(df$as,0.75)-quantile(df$as,0.25))
      +co['mn']*(quantile(df$mn,0.75)-quantile(df$mn,0.25))
      +co['pb']*(quantile(df$pb,0.75)-quantile(df$pb,0.25))

return(est2)

}
```

##Method3. CBPS

```{r}
msm.cbps = function(data = df){
form1 = 'as~age+iq+as.factor(edu)+as.factor(smoke)'
form2 = 'mn~as+age+iq+as.factor(edu)+as.factor(smoke)'
form3 = 'pb~as+age+iq+as.factor(edu)+as.factor(smoke)'

as.ps = CBPS(form1,data = df, method = "exact")
mn.ps = CBPS(form2,data = df, method = "exact")
pb.ps = CBPS(form3,data = df, method = "exact")

weight.mtr = as.ps$weights * mn.ps$weights * pb.ps$weights

msm.cbps <-svyglm(cs~as+mn+pb,design = svydesign(~ 1, weights = ~ weight.mtr,data=df))

res = coef(msm.cbps)

est1 = res['as']*(quantile(df$as,0.75)-quantile(df$as,0.25))
      +res['mn']*(quantile(df$mn,0.75)-quantile(df$mn,0.25))
      +res['pb']*(quantile(df$pb,0.75)-quantile(df$pb,0.25))

return(est1)


}
```

##Method4. Non-parametric CBPS

```{r}
msm.np.cbps = function(data = df){
form1 = 'as~age+iq+as.factor(edu)+as.factor(smoke)'
form2 = 'mn~as+age+iq+as.factor(edu)+as.factor(smoke)'
form3 = 'pb~as+age+iq+as.factor(edu)+as.factor(smoke)'

as.ps = npCBPS(form1,data = df, method = "exact")
mn.ps = npCBPS(form2,data = df, method = "exact")
pb.ps = npCBPS(form3,data = df, method = "exact")

weight.mtr = as.ps$weights * mn.ps$weights * pb.ps$weights

msm.cbps <-svyglm(cs~as+mn+pb,design = svydesign(~ 1, weights = ~ weight.mtr,data=df))

res = coef(msm.cbps)

est1 = res['as']*(quantile(df$as,0.75)-quantile(df$as,0.25))
      +res['mn']*(quantile(df$mn,0.75)-quantile(df$mn,0.25))
      +res['pb']*(quantile(df$pb,0.75)-quantile(df$pb,0.25))

return(est1)


}
```

##Simulation

*true causal effect* : true.holder

*estimated calsal effect by linear regression* : est.holder

*estimated calsal effect by mannual MSM* : msm.holder

*estimated calsal effect by CBPS MSM* : cbps.holder

```{r,results='hide'}
n=825
set.seed(1234)
#simulation = 100
nsim = 10
est.holder = rep(NA,nsim)
true.holder = rep(NA,nsim)
msm.holder = rep(NA,nsim)
cbps.holder = rep(NA,nsim)
np.cbps.holder = rep(NA,nsim)
for(i in 1:nsim){ 
set.seed(1234+i)
df = data_generation()

#true ace
true.holder[i] = (-0.05)*(quantile(df$as,0.75)-quantile(df$as,0.25))
                  +(-0.7)*(quantile(df$mn,0.75)-quantile(df$mn,0.25))
                  +(-0.023)*(quantile(df$pb,0.75)-quantile(df$pb,0.25))

#Method1
est.holder[i] = re.est(df,n = n)
#Method2
msm.holder[i] = msm.mann(df)
#Method3
cbps.holder[i] = msm.cbps(df)
#Method4
np.cbps.holder[i] = msm.np.cbps(df)
}

```

##Statistics and Distribution of Coefficients

```{r}
par(mfrow = c(2,3))
#################################################################
########ESTIMATED Causal effect of 75% -25% exposure#############
hist(est.holder)
hist(msm.holder)
hist(cbps.holder)
hist(np.cbps.holder)
hist(true.holder)
##################




```


```{r}
# 
# bias = est.holder-true.holder
# hist(bias)
# var(est.holder)
# var(true.holder)
# hist(est.holder)

```

reference

[psw](https://www.cebma.org/wp-content/uploads/Li-Using-the-Propensity-Score-Method-to-Estimate-Causal-Effects.pdf)

