---
title: "0303_coding"
author: "Xinyao Wu"
date: "3/4/2020"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(MASS)
library(twang)
library(CBPS)
```

##Data generation

```{r}
data_generation = function(){
#confoundings
age = rnorm(825,22.9,4.2)
iq = rnorm(825,26,5)
edu = rbinom(825,1,0.24)
smoke = rbinom(825,1,0.8)
obs = data.frame(age,iq,edu,smoke)
#a
as = age*0.002+iq*0.02+edu*0.02+smoke*0.1+rnorm(825,0,0.05)
mn = 0.043*as+age*0.02+edu*0.02+iq*0.02+smoke*0.02+rnorm(825,0,0.05)
pb = 0.08*mn+age*0.02+edu*0.02+iq*0.02+smoke*0.02+rnorm(825,0,0.02)
#y
cs = -0.05*as-0.7*mn-0.023*pb+iq+age+edu+0.01*age*iq+0.01*edu*iq-smoke +rnorm(825,0,sd = 0.03)
df = data.frame(as,mn,pb,obs,cs)
return(df)
}
###test = data_generation()

```

## ACE calculation function(regression)
```{r regression}
re.est = function(df,n){
### Method1. Regression 
  
fit = lm(cs~as+mn+pb+age*iq+as.factor(edu)*iq+as.factor(smoke)^2,data = df)

obs = df[4:7]
as = pull(df,as)
mn = pull(df,mn)
pb = pull(df,pb)

as.q = quantile(as,c(0.25,0.75))
mn.q = quantile(mn,c(0.25,0.75))
pb.q = quantile(pb,c(0.25,0.75))

as = rep(as.q[1],n)
mn = rep(mn.q[1],n)
pb = rep(pb.q[1],n)
new1 = data.frame(as,mn,pb,obs)
yhat_25 = predict(fit,new1,type = 'response')

as = rep(as.q[2],n)
mn = rep(mn.q[2],n)
pb = rep(pb.q[2],n)
new2 = data.frame(as,mn,pb,obs)
yhat_75 = predict(fit,new2,type = 'response')

ace = mean(yhat_75)-mean(yhat_25)
return(ace)

}
```

###Method2. MSM(function)

[IPW reference](https://meghapsimatrix.com/post/continuous-r-rmarkdown/)

```{r}

ipw = function(x,df,form){
# the numerator
mod_num <- lm(x ~ 1, data = df)

num <- dnorm(x = x, # treatment 
             mean = fitted.values(mod_num), # fitted values
             sd = summary(mod_num)$sigma) # model sigma
# the demonimator
mod_den <- lm(formula = form, data = df)

den <- dnorm(x = x, # treatment variable
             mean = fitted.values(mod_den), # fitted values
             sd = summary(mod_den)$sigma)
ipw_s = num/den
return(ipw_s)
}

```

### Marginal Structure Model

```{r}
msm.mann = function(data = df){
#test
form1 = 'as~age+iq+as.factor(edu)+as.factor(smoke)'
form2 = 'mn~as+age+iq+as.factor(edu)+as.factor(smoke)'
form3 = 'pb~as+age+iq+as.factor(edu)+as.factor(smoke)'
asw = ipw(df$as,df,form1)
mnw = ipw(df$mn,df,form2)
pbw = ipw(df$pb,df,form3)

#weight matrix
weight.matrix = asw*mnw*pbw

msm <-svyglm(cs~as+mn+pb,design = svydesign(~ 1, weights = ~ weight.matrix,data=df))
res = coef(msm)[2:4]
res = as.data.frame(res) %>% t()
return(res)
}
```

##Method3. CBPS

```{r}
msm.cbps = function(data = df){
form1 = 'as~age+iq+as.factor(edu)+as.factor(smoke)'
form2 = 'mn~as+age+iq+as.factor(edu)+as.factor(smoke)'
form3 = 'pb~as+age+iq+as.factor(edu)+as.factor(smoke)'
as.ps = CBPS(form1,data = df, method = "exact")
mn.ps = CBPS(form2,data = df, method = "exact")
pb.ps = CBPS(form3,data = df, method = "exact")

weight.mtr = as.ps$weights * mn.ps$weights * pb.ps$weights

msm.cbps <-svyglm(cs~as+mn+pb,design = svydesign(~ 1, weights = ~ weight.mtr,data=df))
res2 = coef(msm.cbps)[2:4] 
res2 = as.data.frame(res2) %>% t()
return(res2)
}
```


##Simulation

*true causal effect* : true.holder

*estimated calsal effect by linear regression* : est.holder

*estimated calsal effect by mannual MSM* : man.holder

*estimated calsal effect by CBPS MSM* : cbps.holder

```{r warning=False}
n=825
set.seed(1234)
#simulation = 100
nsim = 10
est.holder = rep(NA,nsim)
true.holder = rep(NA,nsim)
coef.cpbs = c(as=NA,mn = NA,pb= NA)
coef.msm = c(as=NA,mn = NA,pb= NA)

for(i in 1:nsim){ 
set.seed(1234+i)
df = data_generation()

#true ace
true.holder[i] = 0.05*(quantile(df$as,0.75)-quantile(df$as,0.25))+0.7*(quantile(df$mn,0.75)-quantile(df$mn,0.25))-0.023*(quantile(df$pb,0.75)-quantile(df$pb,0.25))

#Method1
est.holder[i] = re.est(df,n = n)
#Method2
coef.msm = rbind(coef.msm,msm.mann(df))
#Method3
coef.cpbs = rbind(coef.cpbs,msm.cbps(df))

}



```

##Statistics and Distribution of Coefficients

```{r}
par(mfrow = c(2,3))
####### CBPS #########
coef.cpbs = coef.cpbs[-1,]
hist(coef.cpbs[,1],main = 'Distribution of (CBPS)coefficient of AS')
hist(coef.cpbs[,2],main = 'Distribution of (CBPS)coefficient of MN')
hist(coef.cpbs[,3],main = 'Distribution of (CBPS)coefficient of PB')
#####################
###### Mannual ######
coef.msm = coef.msm[-1,]
hist(coef.msm[,1],main = 'Distribution of coefficient of AS')
hist(coef.msm[,2],main = 'Distribution of coefficient of MN')
hist(coef.msm[,3],main = 'Distribution of coefficient of PB')

#################################################################
########ESTIMATED Causal effect of 75% -25% exposure#############







##################







```
```{r}

bias = est.holder-true.holder
hist(bias)
var(est.holder)
var(true.holder)
hist(est.holder)

```

#stuck:

I think for each simulation, we should directly get estimated causal effect instead of only get coefficients. Because we generated dataset each time.

