---
title: 'scenario2'
author: "uni:xw2598"
date: "6/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(MASS)
library(twang)
library(CBPS)
library(parallel) # one of the core R packages
library(doParallel)
library(foreach)
library(iterators)
nCores <- 4  # to set manually
registerDoParallel(nCores) 
```


#1.Paramters setting
##scenario 2
```{r}
#population
npop = 1000000

#as = age
coef.as = rbind(0.058) 
# mn = edu+smoke
coef.mn = rbind(0.043,0.02)
# pb = iq
coef.pb = rbind(0.183)
#cs = as+mn+pb+iq+age+edu+age*iq+edu*iq-smoke
coef.cs = rbind(-0.05,-0.7,-0.023,1,1,1,0.01,0.01,-1)
#error
r.err = 0.05
```

#2.Generate population 

```{r,cache=TRUE}
population = function(npop){
#confoundings
age = rnorm(npop,9,4.2)
iq = rnorm(npop,26,5)
edu = rbinom(npop,1,0.24)
smoke = rbinom(npop,1,0.8)
obs = data.frame(age,iq,edu,smoke)
#a
as = cbind(age) %*% coef.as + rnorm(npop,0,r.err)
mn = cbind(edu,smoke) %*% coef.mn + rnorm(npop,0,r.err)
pb = cbind(iq) %*% coef.pb + rnorm(npop,0,r.err)
#y
cs = cbind(as,mn,pb,iq,age,edu,age*iq,edu*iq,smoke) %*% coef.cs +rnorm(npop,0,r.err)

df = data.frame(as,mn,pb,obs,cs)

return(df)
}

df.pop = population(npop)
#scenario1
write.csv(df.pop,'./data/pop_scenario3.csv')

par(mfrow=c(3,3))
#data visualization 
for(i in 1:ncol(df.pop)) {
  hist(df.pop[,i], 
       main = substitute(paste('Histogram of ',a),list(a = colnames(df)[i])),
       xlab = substitute(a,list(a = colnames(df)[i])))
}
```

#3. True Effect

```{r}
true.effect =  apply(cbind(df.pop$as,df.pop$mn,df.pop$pb),2,quantile,0.75)%*% coef.cs[1:3,]- apply(cbind(df.pop$as,df.pop$mn,df.pop$pb),2,quantile,0.25)%*% coef.cs[1:3,]

print(paste('True causal effect is :',true.effect))
```

#4. Method1. Linear regression 

##4-1. Function

```{r regression}
re.est = function(df,size){

fit = lm(cs~as+mn+pb+age*iq+as.factor(edu)*iq+as.factor(smoke)^2,data = df)

obs = df[4:7]
as = pull(df,as)
mn = pull(df,mn)
pb = pull(df,pb)

as.q = quantile(as,c(0.25,0.75))
mn.q = quantile(mn,c(0.25,0.75))
pb.q = quantile(pb,c(0.25,0.75))

as = rep(as.q[1],size)
mn = rep(mn.q[1],size)
pb = rep(pb.q[1],size)
new1 = data.frame(as,mn,pb,obs)
yhat_25 = predict(fit,new1,type = 'response')

as = rep(as.q[2],size)
mn = rep(mn.q[2],size)
pb = rep(pb.q[2],size)
new2 = data.frame(as,mn,pb,obs)
yhat_75 = predict(fit,new2,type = 'response')

ace = mean(yhat_75)-mean(yhat_25)
return(ace)
}
```

##4-2.Check Linear Regression method work 

```{r}
nsim = 100
size = 1000
tolerance = 0.01

#linear.method.check = function(df.pop,nsim,size,tol) {
re.holder = rep(NA,nsim)
for (i in 1:nsim) {
  set.seed(1234+i)
  sdf = sample_n(df.pop,size,replace = F)
  #Method1
  re.holder[i] = re.est(sdf,size)
}

linear.bias = re.holder - true.effect
hist(linear.bias,main = 'Histogram of bias for Linear regression')

#accuracy = sum(ifelse(bias<tol,1,0))/nsim
#print(paste('Accuracy is :',accuracy,'with the tolerance',tol))

#}
#test
#linear.method.check(df.pop,nsim,size,tolerance)
```


#5.Method2.MSM

##5-1 function

###5-1-1 inverse propensity score calculation

```{r}

ipw = function(x,df,form){
# the numerator
mod_num <- lm(x ~ 1, data = df)

num <- dnorm(x = x, # treatment 
             mean = fitted.values(mod_num), # fitted values
             sd = summary(mod_num)$sigma) # model sigma
# the demonimator
mod_den <- lm(formula = form, data = df)

den <- dnorm(x = x, # treatment variable
             mean = fitted.values(mod_den), # fitted values
             sd = summary(mod_den)$sigma)
ipw_s = num/den
return(ipw_s)
}

```

###5-1-2 msm function

```{r}
msm.mann = function(sdf) {
#test
form1 = 'as~age'
form2 = 'mn~as.factor(edu)+as.factor(smoke)'
form3 = 'pb~iq'
asw = ipw(sdf$as,sdf,form1)
mnw = ipw(sdf$mn,sdf,form2)
pbw = ipw(sdf$pb,sdf,form3)

#weight matrix
weight.matrix = asw*mnw*pbw

msm <-svyglm(cs~as+mn+pb,design = svydesign(~ 1, weights = ~ weight.matrix,data=sdf))
             
quant75 = apply(cbind(sdf$as,sdf$mn,sdf$pb),2,quantile,0.75)
as = quant75[1]
mn = quant75[2]
pb = quant75[3]
new1 = data.frame(as,mn,pb)
yhat_75 = predict(msm,new1,type = 'response')
quant25 = apply(cbind(sdf$as,sdf$mn,sdf$pb),2,quantile,0.25)
as = quant25[1]
mn = quant25[2]
pb = quant25[3]
new1 = data.frame(as,mn,pb)
yhat_25 = predict(msm,new1,type = 'response')
est2 = yhat_75 - yhat_25

return(est2)

}



```



##5-2 Check MSM work
  
```{r}
nsim = 10
size = 5000
  
msm.holder = rep(NA,nsim)

for (i in 1:nsim) {
  
  set.seed(1234+i)
  sdf = sample_n(df.pop,size,replace = F)
  #Method2
  msm.holder[i] = msm.mann(sdf)
}

bias = msm.holder - true.effect
hist(bias,main = 'Histogram of bias for MSM')

```

#6.Method 3. CBPS MSM

##6-1 function

```{r}
msm.cbps = function(sdf){
form1 = 'as~age'
form2 = 'mn~as.factor(edu)+as.factor(smoke)'
form3 = 'pb~iq'
as.ps = CBPS(form1,data = sdf, method = "exact")
mn.ps = CBPS(form2,data = sdf, method = "exact")
pb.ps = CBPS(form3,data = sdf, method = "exact")

weight.mtr = as.ps$weights * mn.ps$weights * pb.ps$weights

msm.cbps <-svyglm(cs~as+mn+pb,design = svydesign(~ 1, weights = ~ weight.mtr,data=sdf))

quant75 = apply(cbind(sdf$as,sdf$mn,sdf$pb),2,quantile,0.75)
as = quant75[1]
mn = quant75[2]
pb = quant75[3]
new1 = data.frame(as,mn,pb)

yhat_75 = predict(msm.cbps,new1,type = 'response')


quant25 = apply(cbind(sdf$as,sdf$mn,sdf$pb),2,quantile,0.25)
as = quant25[1]
mn = quant25[2]
pb = quant25[3]
new1 = data.frame(as,mn,pb)
yhat_25 = predict(msm.cbps,new1,type = 'response')

est1 = yhat_75 - yhat_25
return(est1)

}

```

##6-2Check CBPS.MSM work

```{r}
nsim = 100
size = 5000
tolerance = 0.01

cbps.msm.check = function(df.pop,nsim,size,tol) {
  
cbps.msm.holder = rep(NA,nsim)

for (i in 1:nsim) {
  
  set.seed(1234+i)
  sdf = sample_n(df.pop,size,replace = F)
  #Method2
  cbps.msm.holder[i] = msm.cbps(sdf)
}
bias = cbps.msm.holder - true.effect
hist(bias,main = 'Histogram of bias for CBPS MSM')

accuracy = sum(ifelse(bias<tol,1,0))/nsim
print(paste('Accuracy is :',accuracy,'with the tolerance',tol))

}
#test
msm.check(df.pop,nsim,size,tol=1)
```

#7 Method4. Non-parametric CBPS MSM

##7-1 function

```{r}
msm.np.cbps = function(sdf){
form1 = 'as~age'
form2 = 'mn~as.factor(edu)+as.factor(smoke)'
form3 = 'pb~iq'
as.ps = npCBPS(form1,data = sdf, method = "exact")
mn.ps = npCBPS(form2,data = sdf, method = "exact")
pb.ps = npCBPS(form3,data = sdf, method = "exact")

weight.mtr = as.ps$weights * mn.ps$weights * pb.ps$weights


msm.cbps <-svyglm(cs~as+mn+pb,design = svydesign(~ 1, weights = ~ weight.mtr,data=sdf))

quant75 = apply(cbind(sdf$as,sdf$mn,sdf$pb),2,quantile,0.75)
as = quant75[1]
mn = quant75[2]
pb = quant75[3]
new1 = data.frame(as,mn,pb)

yhat_75 = predict(msm.cbps,new1,type = 'response')


quant25 = apply(cbind(sdf$as,sdf$mn,sdf$pb),2,quantile,0.25)
as = quant25[1]
mn = quant25[2]
pb = quant25[3]
new1 = data.frame(as,mn,pb)
yhat_25 = predict(msm.cbps,new1,type = 'response')

est1 = yhat_75 - yhat_25
return(est1)
}

```

##7-2. Check Non-parametric CBPS MSM


```{r}
nsim = 10
size = 1000

npcbps.msm.check = function(df.pop,nsim,size,tol) {
  
npcbps.msm.holder = rep(NA,nsim)

for (i in 1:nsim) {
  
  set.seed(1234+i)
  sdf = sample_n(df.pop,size,replace = F)
  #Method2
  npcbps.msm.holder[i] = msm.np.cbps(sdf)
}
bias = npcbps.msm.holder - true.effect
hist(bias,main = 'Histogram of bias for CBPS MSM')

accuracy = sum(ifelse(bias<tol,1,0))/nsim
print(paste('Accuracy is :',accuracy,'with the tolerance',tol))

}
#test
npcbps.msm.check(df.pop,nsim,size,tol=1)
```


#8.Truncation

##lower_truncation

deleting q% of the lower area data

###8-1-2 mannual marginal structural model

```{r}
msm.mann = function(sdf,q) {
#test
form1 = 'as~age'
form2 = 'mn~as.factor(edu)+as.factor(smoke)'
form3 = 'pb~iq'
asw = ipw(sdf$as,sdf,form1)
mnw = ipw(sdf$mn,sdf,form2)
pbw = ipw(sdf$pb,sdf,form3)
#weight matrix
weight.matrix = asw*mnw*pbw
#truncation
sdf_t = cbind(sdf,asw,mnw,pbw,weight.matrix) %>% as.data.frame() %>% filter(weight.matrix>=quantile(weight.matrix,q))

msm <-svyglm(cs~as+mn+pb,design = svydesign(~ 1, weights = ~ weight.matrix,data=sdf_t))

quant75 = apply(cbind(sdf_t$as,sdf_t$mn,sdf_t$pb),2,quantile,0.75)
as = quant75[1]
mn = quant75[2]
pb = quant75[3]
new1 = data.frame(as,mn,pb)
yhat_75 = predict(msm,new1,type = 'response')
quant25 = apply(cbind(sdf_t$as,sdf_t$mn,sdf_t$pb),2,quantile,0.25)
as = quant25[1]
mn = quant25[2]
pb = quant25[3]
new1 = data.frame(as,mn,pb)
yhat_25 = predict(msm,new1,type = 'response')
est2 = yhat_75 - yhat_25
res = data.frame(q,est2)
return(res)
}


##0~20%
man_trun  = data.frame()
for(j in 1:5){
  q = j/25

for (i in 1:nsim) {
  
  set.seed(1234+i)
  sdf = sample_n(df.pop,size,replace = F)
  man_trun = rbind(man_trun,msm.mann(sdf,q))
}

}

write.csv(man_trun,'./data/lower_truncation_mann_sce3.csv')
```


##upper_truncation

 deleting q% of the upper area data

###8-1-2 mannual marginal structural model

```{r}
msm.mann = function(sdf,q) {
#test
form1 = 'as~age'
form2 = 'mn~as.factor(edu)+as.factor(smoke)'
form3 = 'pb~iq'
asw = ipw(sdf$as,sdf,form1)
mnw = ipw(sdf$mn,sdf,form2)
pbw = ipw(sdf$pb,sdf,form3)
#weight matrix
weight.matrix = asw*mnw*pbw
#truncation
sdf_t = cbind(sdf,asw,mnw,pbw,weight.matrix) %>% as.data.frame() %>% filter(weight.matrix<=quantile(weight.matrix,1-q))

msm <-svyglm(cs~as+mn+pb,design = svydesign(~ 1, weights = ~ weight.matrix,data=sdf_t))

quant75 = apply(cbind(sdf_t$as,sdf_t$mn,sdf_t$pb),2,quantile,0.75)
as = quant75[1]
mn = quant75[2]
pb = quant75[3]
new1 = data.frame(as,mn,pb)
yhat_75 = predict(msm,new1,type = 'response')
quant25 = apply(cbind(sdf_t$as,sdf_t$mn,sdf_t$pb),2,quantile,0.25)
as = quant25[1]
mn = quant25[2]
pb = quant25[3]
new1 = data.frame(as,mn,pb)
yhat_25 = predict(msm,new1,type = 'response')
est2 = yhat_75 - yhat_25
res = data.frame(q,est2)
return(res)
}


##0~20%
man_trun  = data.frame()
for(j in 1:5){
  q = j*4/100

for (i in 1:nsim) {
  
  set.seed(1234+i)
  sdf = sample_n(df.pop,size,replace = F)
  man_trun = rbind(man_trun,msm.mann(sdf,q))
}

}

write.csv(man_trun,'./data/upper_truncation_mann_sce3.csv')
```
































