---
title: "data visualization"
author: "uni:xw2598"
date: "2020/6/19"
output: html_document
---
```{r,include=FALSE}
library(tidyverse)
library(plot3D)
```

#Requirement

- Scenario1_singlesim.csv

- Scenario2_singlesim.csv

- Scenario3_singlesim.csv

- upper_truncation_sce1.csv

- upper_truncation_sce2.csv

- upper_truncation_sce3.csv

- lower_truncation_sce1.csv

- lower_truncation_sce2.csv

- lower_truncation_sce3.csv

All of the data above generated from scenario1.rmd,scenario2.rmd,scenario2.rmd and stored in data folder.

#Scenario1

##1.Density plot

```{r}
df = read.csv('./data/scenario1_singlesim.csv')

ggplot(df)+geom_point(aes(x = asw,y = pbw,color = mnw))
ggplot(df)+geom_point(aes(x = asw,y = mnw,color = pbw))
ggplot(df)+geom_point(aes(x = pbw,y = pbw,color = asw))

```

##2.3D Plot

```{r}

scatter3D(df$as, df$mn, df$ps, colvar = df$pb,phi = 20, theta = 15, bty = "b2", ticktype = "detailed",main = "weight distribution for scenario 1", xlab = "As",ylab ="mn", zlab = "propensity score")

scatter3D(df$mn, df$pb, df$ps, colvar = df$as,phi = 20, theta = 15, bty = "b2", ticktype = "detailed",main = "weight distribution for scenario 1", xlab = "As",ylab ="mn", zlab = "propensity score")

scatter3D(df$as, df$pb, df$ps, colvar = df$mn,phi = 20, theta = 15, bty = "b2", ticktype = "detailed",main = "weight distribution for scenario 1", xlab = "As",ylab ="mn", zlab = "propensity score")
```

##3.Quantified Truncation

###3-1.upper truncation
```{r}


```


































