---
title: "data visualization"
author: "uni:xw2598"
date: "2020/6/19"
output: html_document
---
```{r,include=FALSE}
library(tidyverse)
library(plot3D)
```

#Requirement

- Scenario1_singlesim.csv

- Scenario2_singlesim.csv

- Scenario3_singlesim.csv

- upper_truncation_sce1.csv

- upper_truncation_sce2.csv

- upper_truncation_sce3.csv

- lower_truncation_sce1.csv

- lower_truncation_sce2.csv

- lower_truncation_sce3.csv

All of the data above generated from scenario1.rmd,scenario2.rmd,scenario2.rmd and stored in data folder.

#Scenario1

##1.Density plot

```{r}
df = read.csv('./data/scenario1_singlesim.csv')

ggplot(df)+geom_point(aes(x = asw,y = pbw,color = mnw))
ggplot(df)+geom_point(aes(x = asw,y = mnw,color = pbw))
ggplot(df)+geom_point(aes(x = pbw,y = pbw,color = asw))

```

##2.3D Plot

```{r}

scatter3D(df$as, df$mn, df$ps, colvar = df$pb,phi = 20, theta = 15, bty = "b2", ticktype = "detailed",main = "weight distribution for scenario 1", xlab = "As",ylab ="mn", zlab = "propensity score")

scatter3D(df$mn, df$pb, df$ps, colvar = df$as,phi = 20, theta = 15, bty = "b2", ticktype = "detailed",main = "weight distribution for scenario 1", xlab = "As",ylab ="mn", zlab = "propensity score")

scatter3D(df$as, df$pb, df$ps, colvar = df$mn,phi = 20, theta = 15, bty = "b2", ticktype = "detailed",main = "weight distribution for scenario 1", xlab = "As",ylab ="mn", zlab = "propensity score")
```

##3.Quantified Truncation

###3-1.lower truncation
```{r}
low1= read.csv("./data/lower_truncation_mann_sce1.csv")
low1$sce = 'scenario1'
low2 = read.csv("./data/lower_truncation_mann_sce2.csv")
low2$sce = 'scenario2'
low3 = read.csv("./data/lower_truncation_mann_sce3.csv")
low3$sce = 'scenario3'
low = rbind(low1,low2,low3)
low = low%>% group_by(q,sce) %>% summarise(avg = mean(response),sd = sd(response)) 
knitr::kable(low)
ggplot(low)+geom_line(aes(x = q,y = avg,color = sce))
ggplot(low)+geom_line(aes(x = q,y = sd,color = sce))
```


```{r}
up1= read.csv("./data/upper_truncation_mann_sce1.csv")
up1$sce = 'scenario1'
up2 = read.csv("./data/upper_truncation_mann_sce2.csv")
up2$sce = 'scenario2'
up3 = read.csv("./data/upper_truncation_mann_sce3.csv")
up3$sce = 'scenario3'
up= rbind(up1,up2,up3)
up = up%>% group_by(q,sce) %>% summarise(avg = mean(response),sd = sd(response)) 
knitr::kable(up)
ggplot(up)+geom_line(aes(x = q,y = avg,color = sce))
ggplot(up)+geom_line(aes(x = q,y = sd,color = sce))
```































